Irt plot extra

### 2022-03-30 manuscript.Rmd
Discussion Updated

**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.

@@

In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`. All the items in this factor stemmed from the individual's preference of using blue light filters in different light environments. The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`. Items under this factor investigated individuals' hours spent outdoor. The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance. Items under this factor dealt with the specific behaviours pertaining to using phone and smart-watch in bed. The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`. The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`. These five items investigated the behaviours related to individual's light exposure before bedtime. Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance. This factor captured individual's morning and daytime light exposure related behaviour. The internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)`. It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behaviour, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse coded these two items.

@@

## Secondary Analysis: Semantic Scale Network and Grade Level

Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarities lie between .47 to .51. Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.

```{r textanalysis, include=F}
#This chunk holds codes for semantic analysis and readability test

@@

Though there are lots of validated scale to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure. At present there is a dearth of validated scale to measure light exposure related behaviours. In that vein we have developed a subjective self-reported scale that can capture light exposure related behaviour in different dimensions.

Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments. A large scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from large sample (n=`r nrow(EFA.descriptives)`) to explore the latent structure. Exploratory factor analysis revealed a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime", and "Using light in the morning and during daytime"). The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`. As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

<!-- A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item. The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa(residual.fitm[6,1],2,F)`). -->

<!-- The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI. Items in those two scales were looking into behaviours related to sleep. As such the similarity index obtained is expected. Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33. -->

<!-- We developed a short-LEBA (18 items) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`). We discarded five items with relatively flat item information curve [I($\theta$) <.20]. IRT analysis indicated short form of LEBA is a psychometrically sound measure. Item fit indexes and person fit index for all five fitted model were acceptable. Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour. Test information curve also indicated a good coverage of underlying trait continuum with precision. -->

LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health. All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.

@@

We developed a novel self-reported subjective scale-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour. We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey. Our EFA gave a five solution with 25 items. A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity). A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18-item scale with a good coverage across the underlying trait continuum. Hence, we could recommend that LEBA can be used to measure different aspects of light exposure related behaviour.

>>>>

**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new]. Also, we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.

@@

In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`. All the items in this factor stemmed from the individual's preference of using blue light filters in different light environments. The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`. Items under this factor investigated individuals' hours spent outdoor. The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance. Items under this factor dealt with the specific behaviours pertaining to using phone and smart-watch in bed. The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`. The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`. These five items investigated the behaviours related to individual's light exposure before bedtime. Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance. This factor captured individual's morning and daytime light exposure related behaviour. The internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)`. It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behaviour, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse coded these two items. Internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarities lie between .47 to .51. 
```{r textanalysis, include=F}
#This chunk holds codes for semantic analysis and readability test

@@

Though there are lots of validated scale to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure. In that vein we have developed a subjective self-reported scale that can capture light exposure related behaviour in different dimensions.

Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments. A large-scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from a large sample (n=`r nrow(data)`). Data collected on the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). Exploratory factor analysis revealed a five factor solution with 25 items. ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime", and "Using light in the morning and during daytime"). The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`. Except for the fifth factor the internal reliability coefficients were above .70. For the fifth factor it was `r apa((alpha.tab[5,1]),2,F)`. As a rule of thumb reliability coefficient higher than .70 is considered to be satisfactory. However for scales with less than 20 items and at the early developmental stage, a value of .50 is also acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Also all of the factors were highly interpretable in terms of a common theme and contributed essentially towards our aim to capture light exposure related behaviour. This eventually led us to accept this five-factor structure. The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$ = `r apa(omega$omega.tot,2,T)`).

Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity. However, two items were removed from the solution due their less contribution to the model (item 37 & 26). The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`). On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" holds the true across native and non-native English speakers. This indicates the applicability of LEBA on both native and non-native English Speakers. However, this brings up another question to be answered, what is the required grade level to understand the items of our scale? To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method. Our scale is will appear understandable to those who are at least a grade four student and have a age of at least 8.33 years. As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic]. "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI. However, the aim of those scale and ours was different. Items in those two scales were looking into behaviours related to sleep whereas our  aim was to capture light exposure related behaviour.

lastly, we developed a short-LEBA (18 items) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`). We discarded five items (1, 25, 38, 30, & 41) with relatively flat item information curve [I($\theta$) <.20]. Test information curves indicated short form of LEBA is a psychometrically sound measure with adequate coverage of underlying traits to capture different extents of light exposure related behaviours with precision. Item fit index and person fit index for all five fitted model were acceptable providing evidence of validity of our models. Items had diverse item discrimination parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.

Based on all the gathered evidences, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health. All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.

@@

We developed a novel self-reported subjective scale-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour. We developed 48 items, judged the relevance and content of the items and conducted a large-scale geographically unrestricted cross-sectional survey. Our EFA gave a five solution with 25 items. A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded. The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity). A short-form of LEBA was developed using IRT analysis. IRT analysis gave a 18-item scale with a good coverage across the underlying trait continuum. Hence, we could recommend that LEBA can be used to profile individuals according to their light exposure related behaviours.
